---
title: "Analysis Script Pilot Indirect Source v1"
author: "Hening Wang"
date: "2024-11-18"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---
Supress messages in this document so that the output is cleaner
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
Import packages.
```{r}
rm(list = ls())

options(warn = -1)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggplot2)
library(aida)
```

Set up theme for ggplot.

```{r}
theme_set(theme_aida())

##################################################
## CSP-colors
##################################################
CSP_colors = c(
  "#7581B3", "#99C2C2", "#C65353", "#E2BA78", "#5C7457", "#575463",
  "#B0B7D4", "#66A3A3", "#DB9494", "#D49735", "#9BB096", "#D4D3D9",
  "#414C76", "#993333"
  )
# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = CSP_colors)
}
scale_fill_discrete <- function(...) {
  scale_fill_manual(..., values = CSP_colors)
}
```

# Data Import & Preprocessing

Import data

```{r}
data <- read.csv("../data/results.csv")
```

Merge decision1 and decision2 into one row by the same submission id
```{r}
data <- data %>% group_by(submission_id, informationSource) %>% 
  summarize(
    decision1 = first(na.omit(decision1)),
    decision2 = first(na.omit(decision2))
  ) %>%
  mutate(update = decision2 - decision1)

```

Factorise variables: id, item, informationSource, listenerRole

```{r}
data$id <- as.factor(1:nrow(data))
data$informationSource <- as.factor(data$informationSource)
```

.


Recruitment criteria: 1. English native speakers 2. Approval rate \> 90%
3. Completion \> 5 times 4. Not included in the prior studies of
CommuniCause

# Plots

## A histogram showing the distribution of probs. 
**Interpretation: Data is left-skewed.**

```{r}
ggplot(data, aes(x = update)) +
  geom_histogram(binwidth = 5, fill = CSP_colors[1]) +
  labs(title = "Distribution of updated probs",
       x = "Updated probs.",
       y = "Frequency")

```

## Plot the dependent variable "probs" against conditions.

**Interpretation:**
```{r}
long_data <- data %>%
  pivot_longer(cols = starts_with("decision"),
               names_to = "decisionType",
               values_to = "probs",
               values_drop_na = TRUE)

p1 <- ggplot(long_data, aes(x = informationSource, y = probs, fill = decisionType)) +
  geom_boxplot() +
  labs(title = "Probs. by information source and decision \n type",
       x = "Information Source",
       y = "Probs.")

ggsave("fig2.png", p1, width = 6, height = 4, dpi = 300)
```



```{r}
p2 <- ggplot(data, aes(x = informationSource, y = update)) +
  geom_boxplot(fill = CSP_colors[1]) + 
  labs(title = "Updated probs by information source",
       x = "Information Source",
       y = "Updated probs.")

ggsave("fig1.png", p2, width = 6, height = 4, dpi = 300)
```

# Statistical Analysis
**Note: Nothing is significant here.** 
```{r}
data_direct <- data$update[data$informationSource == "direct"]
data_indirect <- data$update[data$informationSource == "indirect"]
t.test(data_direct, data_indirect, alternative = "greater")
```

```{r}
t.test(data_indirect, mu = 0, alternative = "greater")
t.test(data_direct, mu = 0, alternative = "greater")
```

```{r}
lm(probs ~ informationSource * decisionType, data = long_data) %>% summary()
```
```{r}
data_decision1_direct <- data$decision1[data$informationSource == "direct"]
data_decision1_indirect <- data$decision1[data$informationSource == "indirect"]
t.test(data_decision1_direct, data_decision1_indirect, alternative = "less")
```
# Power analysis
Compute the effect size of the difference between the two conditions
```{r}
library(effsize)
cohen.d(data_direct, data_indirect)
```
```{r}
library(pwr)
pwr.t.test(d = 0.8, sig.level = 0.05, power = 0.9, type = "two.sample", alternative = "greater")

```
