---
title: "Causal Implicature - Pilot data analysis"
author: "MF"
format: html
editor: visual
---

```{r, echo = F, error=F, warning=F, message=F}
library(tidyverse)
library(tidyboot)
library(aida)
library(brms)
library(faintr)

##################################################

# these options help Stan run faster
options(mc.cores = parallel::detectCores())

# use the aida-theme for plotting
theme_set(theme_aida())

# global color scheme / non-optimized
project_colors = c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")

# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = project_colors)
}
scale_fill_discrete <- function(...) {
  scale_fill_manual(..., values = project_colors)
} 

##################################################

d <- read_csv('01-wrangled-data.csv')
```

## Study details

N=200 participants recruited via Prolific (English Native, at least 10 previous studies, at least 90% approval rate), but only N=195 data sets received (due to technical issues).

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
