---
title: "01-Plots"
output: html_document
---

Supress messages in this document so that the output is cleaner.
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
Import packages.
```{r}
rm(list = ls())
options(warn = -1)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggplot2)
library(aida)
library(BayesFactor)
library(pwr)
library(effsize)
library(HDInterval)
```

Set up theme for ggplot.

```{r}
theme_set(theme_aida())

##################################################
## CSP-colors
##################################################
CSP_colors = c(
  "#7581B3", "#99C2C2", "#C65353", "#E2BA78", "#5C7457", "#575463",
  "#B0B7D4", "#66A3A3", "#DB9494", "#D49735", "#9BB096", "#D4D3D9",
  "#414C76", "#993333"
  )
# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = CSP_colors)
}
scale_fill_discrete <- function(...) {
  scale_fill_manual(..., values = CSP_colors)
}
```

# Data Import 

```{r}
data <- read.csv("./data_preprocessed_allFactors.csv")
```

Show how many pps in each condition.
```{r}
data %>% 
  group_by(informationSource, scienceTeam) %>% 
  summarise(n = n())
```

# Distribution of the data in density plot
```{r}
ggplot(data, aes(x = decision1)) +
  geom_density(fill = CSP_colors[1]) +
  facet_wrap(informationSource ~ scienceTeam, scales = "free_y") +
  labs(title = "Decision1",
       x = "Decision1",
       y = "Density")

```

```{r}
# The data is left-skewed
ggplot(data, aes(x = decision2)) +
  geom_density(fill = CSP_colors[1]) +
  facet_wrap(informationSource ~ scienceTeam, scales = "free_y") +
  labs(title = "Decision2",
       x = "Decision2",
       y = "Density")


ggplot(data, aes(x = decision2)) +
  geom_density(fill = CSP_colors[1]) +
  labs(title = "Decision2",
       x = "Decision2",
       y = "Density")

```
```{r}
ggplot(data, aes(x = update)) +
  geom_density(fill = CSP_colors[1]) +
  facet_wrap(informationSource ~ scienceTeam, scales = "free_y") +
  labs(title = "Update",
       x = "Update",
       y = "Density")
```
# Mean and CIs plot
```{r}
data %>% 
  group_by(informationSource, scienceTeam) %>% 
  summarise(mean_decision1 = mean(decision1),
            mean_decision2 = mean(decision2),
            mean_update = mean(update)) %>% 
  pivot_longer(cols = c(mean_decision1, mean_decision2, mean_update), names_to = "decision", values_to = "mean") %>% 
  ggplot(aes(x = decision, y = mean, fill = informationSource)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  facet_wrap(~scienceTeam) +
  labs(
       x = "Decision",
       y = "Mean") +
  scale_fill_manual(values = CSP_colors)
```
Mean and CIs for decision2 only 
```{r}
data %>% ggplot(aes(x = scienceTeam, y = decision2, color = informationSource)) +
  stat_summary(fun.data = mean_cl_boot, geom = "point", position = position_dodge(0.5), width = 0.5) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2, position = position_dodge(0.5)) +
  labs(x = "Science Team",
       y = "Causal Belief Updated",
       # legend title
       fill = "Information Source"
       ) -> p
p
ggsave("decision2_mean_CI.png", plot = p, width = 8, height = 6, dpi = 300)
```
Update
```{r}
data %>% mutate(scienceTeam_relabel = as.factor(ifelse(scienceTeam == "Localization", "-Alignment", "+Alignment"))
                )%>% ggplot(aes(x = scienceTeam_relabel, y = update, fill = informationSource)) +
  stat_summary(fun.data = mean_cl_boot, geom = "bar", position = position_dodge(0.5), width = 0.5) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2, position = position_dodge(0.5)) +
  labs(x = "Speaker Relevance",
       y = "Causal Confidence in Change",
       # legend title
       fill = "Speaker Addressing"
       ) -> q
q

data %>% ggplot(aes(x = informationSource, y = update, color = scienceTeam)) +
  stat_summary(fun.data = mean_cl_boot, geom = "point", position = position_dodge(0.5), width = 0.5) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2, position = position_dodge(0.5)) +
  labs(x = "Science Team",
       y = "Update of Causal Belief",
       # legend title
       fill = "Information Source"
       )
```

# Inferential Statistics of Decision2
Normality test
```{r}
shapiro.test(data$decision1)
shapiro.test(data$decision2)
# log transformation
print("Log transformation")
shapiro.test(log(data$decision2))

shapiro.test(data$update)
```

Contrast Coding between indirect and direct
```{r}
# Set factor levels explicitly
data$informationSource <- factor(data$informationSource, levels = c("direct", "indirect"))
data$scienceTeam <- factor(data$scienceTeam, levels = c("Localization", "Cultivation"))

# Apply sum contrast coding
contrasts(data$informationSource) <- contr.sum(2)
colnames(contrasts(data$informationSource)) <- "direct_vs_indirect"

contrasts(data$scienceTeam) <- contr.sum(2)
colnames(contrasts(data$scienceTeam)) <- "localization_vs_cultivation"

# Check the contrast coding
contrasts(data$informationSource)
contrasts(data$scienceTeam)
```

## Linear Regression (Frequentist)
```{r}
model_full <- lm(log(decision2) ~  scienceTeam * informationSource, data = data)
summary(model_full)

model_full_decision1 <- lm(decision1 ~ informationSource * scienceTeam, data = data)
summary(model_full_decision1)

model_full_update <- lm(update ~ informationSource * scienceTeam, data = data)
summary(model_full_update)
```
```{r}
model_reduced <- lm(update ~ informationSource + scienceTeam, data = data)
anova(model_full_update, model_reduced)
```
```{r}
plot(model_full_update)
library(sjPlot)

# Plot interaction with scienceTeam on the x-axis
plot_model(model_full_update, type = "int", terms = c("scienceTeam", "informationSource"))
```



## Linear Regression (Bayesian)


```{r}
library(brms)
model_full_bayesian <- brm(
  update ~ informationSource * scienceTeam,
  data = data,
  family = gaussian(),
  sample_prior = "yes",
  prior = c(prior("normal(0, 10)"))
)
#brms::hypothesis(model, "informationSourceindirect < 0")
#faintr::compare_groups(model, lower = informationSource == "indirect", higher = informationSource == "direct", include_bf = TRUE)
```

```{r}
summary(model_full_bayesian)
```

```{r}
brms::pp_check(model_full_bayesian)   # posterior predictive check
```

```{r}
hypothesis(model_full_bayesian, "informationSourcedirect_vs_indirect:scienceTeamlocalization_vs_cultivation > 0")
hypothesis(model_full_bayesian, "informationSourcedirect_vs_indirect > 0")

```
```{r}
library(emmeans)
pairs(emmeans(model_full_bayesian, ~ informationSource | scienceTeam))
emms <- emmeans(model_full_bayesian, ~ informationSource | scienceTeam)
pairs_emms <- contrast(emms, method = "pairwise", infer = c(TRUE, TRUE), type = "response")
faintr::get_cell_definitions(model_full_bayesian)
faintr::compare_groups(model_full_bayesian, lower = informationSource == "indirect" & scienceTeam == "Localization", 
                       higher = informationSource == "direct" & scienceTeam == "Localization", 
                       include_bf = TRUE)

faintr::compare_groups(model_full_bayesian, lower = informationSource == "indirect" & scienceTeam == "Cultivation", 
                       higher = informationSource == "direct" & scienceTeam == "Cultivation", 
                       include_bf = TRUE)

faintr::compare_groups(model_full_bayesian, lower = informationSource == "indirect" & scienceTeam == "Cultivation", 
                       higher = informationSource == "indirect" & scienceTeam == "Localization", 
                       include_bf = TRUE)

faintr::compare_groups(model_full_bayesian, lower = informationSource == "direct" & scienceTeam == "Cultivation", 
                       higher = informationSource == "direct" & scienceTeam == "Localization", 
                       include_bf = TRUE)

faintr::compare_groups(model_full_bayesian, lower = informationSource == "indirect" & scienceTeam == "Cultivation", 
                       higher = informationSource == "direct" & scienceTeam == "Localization", 
                       include_bf = TRUE)



```

Compare indirect Localization and direct Cultivation (the first two conditions collect in the first experiment) 
```{r}
faintr::compare_groups(model_full_bayesian, higher = informationSource == "direct" & scienceTeam == "Cultivation", 
                       lower = informationSource == "indirect" & scienceTeam == "Localization", 
                       include_bf = TRUE)
```


